Fusion Moves for Correlation Clustering

### 2014-11-11 paper/egpaper_for_review.tex
started to change sec. 5, and minor figure fixes

@@

\textbf{new}

Fusion moves as defined in \cite{Lempitsky-2010} work
in the node domain and do not work properly for 
objective functions as Eq.~\ref{eq:nodeproblem} since
the node coloring is ambiguous and has no semantic meaning.
In the following, we propose a more suitable fusion move for correlation
clustering which works on the edge domain.
%
Given two proposal solutions $y'$ and $y''$,
$\mathcal{C}$ is the set of edges
which are uncut in $y'$ and $y''$.
%
\begin{align}
\breve{y}    & =  y' \cup y'' \\
\mathcal{C}  & =  \{ (i, j) \quad | \quad \breve{y}_{ij} = 0 \}
\end{align}
%
The fusion move for correlation clustering is solving Eq.~\ref{eq:edgeproblem}
with additional \emph{must-link constraints} for all edges in $\mathcal{C}$.
%
\begin{align}
  y^* &=& \argmin_{y \in P(G)} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:fusion_move_a}.\\ 
  s.t & &  y_{ij} = 0 \quad \forall (i, j) \in \mathcal{C} \nonumber
\end{align}
%
By construction, solving Eq.~\ref{eq:fusion_move_a} cannot increase the energy:
\begin{align}
  \sum  w_{ij} \cdot y^*_{ij}  \leq \min \left( \sum  w_{ij} \cdot y'_{ij} ,  \sum   w_{ij} \cdot y''_{ij} \right)
\end{align}
%
Eq.~\ref{eq:fusion_move_a} can be solved efficiently, since 
we can work on a coarser graph, where all nodes which are connected
via must-link constraints are merged into single nodes.
This coarser graph is constructed by contracting all must-link edges.

\textbf{old}

Motivation Using Fusion moves -> problem ambiguity

A consistent edge labeling $y$ defines a segmentation of $V$ by enumerating the connected components 
in $G|_y=(V,\{e\in E|y_e=0\}$ by $l_v = \#(v)$, where $\#(v)$ denotes the number of the connected component of the node $v\in V$.

We define the contradiction of graph $G_y=(V_y,E_y)$
with $V_y=\{\#(v)|v\in V\}$ and $E_y=\{\#(v),\#(u)|uv\in E, y_{uv}=1\})$.

@@

@@

% \begin{center}
%     \begin{eqnarray}
%       y \cdot w \leq \min(y'\cdot w,  y'' \cdot w) 
%     \end{eqnarray}
% \end{center}

@@

\noindent \textbf{Desired Properties:}
As discussed in \cite{Lempitsky-2010}, proposals
should have two properties: \emph{quality} 
and \emph{diversity}.
The quality / energy of the individual proposals
ensures low energy solutions since the
result of the fusion cannot be higher then
the energy of the current best solution.
Diversity between the individual proposals
reduces the chances to get stuck in local minima.
For correlation clustering fusion we add a third
property: \emph{size}.
The size of the contraction graph directly
depends on the number of connected components
in the proposal solution and the current best solution.
The extreme  case is a proposal where each 
node is in a separate connnected component.
Solving the fusion move with such a proposal
is equivalent to solving the original problem.
Solving the fusion move with a proposal with 
a single connected component will result 
in the current best solution.
Therefore the size of the proposals
should be small enough, such that solving
eq.~\ref{eq:edgeproblem} can
be done fast enough, but large enough to make
meaningful moves (??? this last sentence needs to be rewritten).

@@

\begin{remark}[Fix-point (pointless to me)]
Let $Y$ be the set of possible proposals, than
$y'$ is a fix-point if $y'=\arg\max_{y\in P(G_{y'\OR y''})} y\cdot w$ for all $y''\in Y$
\end{remark}

>>>>

Fusion moves as defined in \cite{Lempitsky-2010} work
in the node domain and do not work properly for 
objective functions as Eq.~\ref{eq:nodeproblem} since
the node coloring is ambiguous and has no semantic meaning (see Fig.~\ref{fig:fusion_abiguty}).
In the following, we propose a more suitable fusion move for correlation
clustering which works on the edge domain.
%
Given two proposal solutions $y'$ and $y''$,
$\mathcal{C}$ is the set of edges
which are uncut in $y'$ and $y''$.
%
\begin{align}
\breve{y}    & =  y' \cup y'' \\
\mathcal{C}  & =  \{ (i, j) \quad | \quad \breve{y}_{ij} = 0 \}
\end{align}
%
The fusion move for correlation clustering is solving Eq.~\ref{eq:edgeproblem}
with additional \emph{must-link constraints} for all edges in $\mathcal{C}$.
%
\begin{align}
  y^* &=& \argmin_{y \in P(G)} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:fusion_move_a}.\\ 
  s.t & &  y_{ij} = 0 \quad \forall (i, j) \in \mathcal{C} \nonumber
\end{align}
%
By construction, solving Eq.~\ref{eq:fusion_move_a} cannot increase the energy:
\begin{align}
  \sum  w_{ij} \cdot y^*_{ij}  \leq \min \left( \sum  w_{ij} \cdot y'_{ij} ,  \sum   w_{ij} \cdot y''_{ij} \right)
\end{align}
%
Eq.~\ref{eq:fusion_move_a} can be solved efficiently, since 
we can work on a coarser graph, where all nodes which are connected
via must-link constraints are merged into single nodes.
This coarser graph is constructed by contracting all must-link edges.

@@

%\textbf{old}
%
%Motivation Using Fusion moves -> problem ambiguity
%
%A consistent edge labeling $y$ defines a segmentation of $V$ by enumerating the connected components 
%in $G|_y=(V,\{e\in E|y_e=0\}$ by $l_v = \#(v)$, where $\#(v)$ denotes the number of the connected component of the %node $v\in V$.
%
%We define the contradiction of graph $G_y=(V_y,E_y)$
%with $V_y=\{\#(v)|v\in V\}$ and $E_y=\{\#(v),\#(u)|uv\in E, y_{uv}=1\})$.

@@

\subsection{Fast Optimization} \label{sec:fast_optimization}
TODO:
Here we need to proof that it is equivalent 
to optimize the contracted graph !

@@

% \begin{center}
%     \begin{eqnarray}
%       y \cdot w \leq \min(y'\cdot w,  y'' \cdot w) 
%     \end{eqnarray}
% \end{center}
Once we know how to fuse segmentations, the actual algorithm 
for correlation clustering 
is simple and similar to the fusion move algorithm of Lempitsky \etal~\cite{bagon_2011_arxiv}.
We iteratively improve the best solution by
fusing it with proposal solutions.
The inherent difference is how we define the fusion.
We fuse the segmentations according to Eq.~\ref{eq:fusion_move_a}
and optimize the subproblems as described in 
Sec.\ref{sec:fast_optimization}.

@@

As discussed in \cite{Lempitsky-2010}, proposals
should have two properties: \emph{quality} 
and \emph{diversity}.
The quality / energy of the individual proposals
ensures low energy solutions since the
result of the fusion cannot be higher then
the energy of the current best solution.
Diversity between the individual proposals
reduces the chances to get stuck in local minima.
For correlation clustering fusion we add a third
property: \emph{size}.
The size of the contraction graph directly
depends on the number of connected components
in the proposal solution and the current best solution.
The extreme  case is a proposal where each 
node is in a separate connnected component.
Solving the fusion move with such a proposal
is equivalent to solving the original problem.
Solving the fusion move with a proposal with 
a single connected component will result 
in the current best solution.
Therefore the size of the proposals
should be small enough, such that solving
eq.~\ref{eq:edgeproblem} can
be done fast enough, but large enough to make
meaningful moves (??? this last sentence needs to be rewritten).

@@

%\begin{remark}[Fix-point (pointless to me)]
%Let $Y$ be the set of possible proposals, than
%$y'$ is a fix-point if $y'=\arg\max_{y\in P(G_{y'\OR y''})} y\cdot w$ for all $y''\in Y$
%\end{remark}
